---
title: "Final Project"
author: "Mia Krout"
date: "4/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


I load some packages that I may need for this data set. RSocrata is specifically
used for the Chicago Data Portal API data.
```{r libraries for apis, echo=FALSE}
#install.packages(c("httr", "jsonlite", "RSocrata))
library(httr)
library(jsonlite)
library(RSocrata)
library(tidyverse)
library(kableExtra)

#API key ID: 7vwfj55tah2za8t0hmgcwkc2w
#API key secret: 4vxjm7n1v7ddid1vhlx4hvn3v0k9dnagm8hc76xm8m7rsbt7jo
```


Here I call the ridership dataset.
```{r, echo=FALSE}
cta <- read.socrata("https://data.cityofchicago.org/resource/5neh-572f.json")
cta
```

We decided to look at ridership for 7 stations that had projects completed between
2009 and 2019. We chose stations in areas all throughout the city. If I look at
a summary of this data I can see that I have information from Jan 2001 to
Nov 30, 2020. This works for us as we wanted to have data for at least a year
after a projected was completed but before the COVID pandemic affected ridership.
Our most recent project was completed by Feb 2019 so that would give us a years 
worth of data before the pandemic was in play in Chicago.
```{r check out the data}
summary(cta)
```
For our data we will focus on Jarvis station for the Red North Station Interim
Improvements project; the Wilson Station Reconstruction; Clark/Division Station
Renovation; Addison as part of Blue Line projects; Cermak-Chinatown Station
Renovation; Garfield Station as part of the Red Line South Station Improvements;
and the 95th Dan Ryan Terminal Reconstruction Project. I filter the data for
the stations I want to include and to only show weekday ride counts. This has 
ride data by each weekday for every station. On the rail system, a customer is 
counted as an "entry" each time he or she passes through a turnstile to enter 
a station.  Customers are not counted as "entries" when they make a 
"cross-platform" transfer from one rail line to another, since they don't pass 
through a turnstile. Where the number given for rail is in "boardings" what's 
presented is a statistically valid estimate of the actual number of boardings 
onto the rail system.
```{r filter for our stations and by weekday rides}
cta1 <- as_tibble(
  cta %>%
  group_by(station_id) %>%
  filter(station_id %in% c("41190", "40540", "40630", "41240",
                            "41000", "41170", "40450"),
         daytype == "W") %>% #W is the weekday ridership information
  mutate(date = as.Date(date),
         rides = as.numeric(rides))
)
cta1
```

The dates are presented in year-month-day format in one column which is great for when I look at
ranges of ridership. But I want to report station averages by month so I'm going to
separate the date into new columns so I can filter my data.
```{r filtering for the data I want and new date columns}
cta2 <- 
  cta1 %>%
  group_by(stationname, date, rides) %>%
  filter(date >= as.Date("2008-10-01") & date <= as.Date("2020-01-31")) %>%
  mutate(month = format(date, "%m"), year = format(date, "%Y"))
cta2
```

Specific month for beginning of Addison project was unavailable, Fall 2015 was the
information we had so we chose to look at ridership between Oct 2014- Oct 2015.
```{r ridership averages by station}
Cer_Chi <- 
  cta2 %>%
  filter(stationname == "Cermak-Chinatown") %>%
  group_by(month) %>%
  summarise(Cer_Chi_bef = mean(rides[date > as.Date("2008-10-01") & date < as.Date("2009-11-01")]),
            Cer_Chi_aft = mean(rides[date > as.Date("2011-04-30") & date < as.Date("2012-05-01")])) %>% 
  mutate(diff_mean = Cer_Chi_aft - Cer_Chi_bef,
         perc_mean = ((Cer_Chi_aft - Cer_Chi_bef)/ Cer_Chi_bef)*100)
Cer_Chi

Clark_Div <- 
  cta2 %>%
  filter(stationname == "Clark/Division") %>%
  group_by(month) %>%
  summarise(Clark_Div_bef = mean(rides[date > as.Date("2011-09-01") & date < as.Date("2012-09-01")]),
            Clark_Div_aft = mean(rides[date > as.Date("2015-09-30") & date < as.Date("2016-10-01")])) %>% 
  mutate(diff_mean = Clark_Div_aft - Clark_Div_bef,
         perc_mean = ((Clark_Div_aft - Clark_Div_bef)/ Clark_Div_bef)*100)
Clark_Div

Jarvis <- 
  cta2 %>%
  filter(stationname == "Jarvis") %>%
  group_by(month) %>%
  summarise(Jarvis_bef = mean(rides[date > as.Date("2011-11-01") & date < as.Date("2012-11-01")]),
            Jarvis_aft = mean(rides[date > as.Date("2012-12-31") & date < as.Date("2014-01-01")])) %>% 
  mutate(diff_mean = Jarvis_aft - Jarvis_bef,
         perc_mean = ((Jarvis_aft - Jarvis_bef)/ Jarvis_bef)*100)
Jarvis

Garfield <- 
  cta2 %>%
  filter(stationname == "Garfield-Dan Ryan") %>%
  group_by(month) %>%
  summarise(Garf_bef = mean(rides[date > as.Date("2012-05-01") & date < as.Date("2013-05-01")]),
            Garf_aft = mean(rides[date > as.Date("2013-10-31") & date < as.Date("2014-11-01")])) %>%
  mutate(diff_mean = Garf_aft - Garf_bef,
         perc_mean = ((Garf_aft - Garf_bef)/ Garf_bef)*100)
Garfield

Wilson <- 
  cta2 %>%
  filter(stationname == "Wilson") %>%
  group_by(month) %>%
  summarise(Wilson_bef = mean(rides[date > as.Date("2013-09-30") & date < as.Date("2014-10-01")]),
            Wilson_aft = mean(rides[date > as.Date("2017-10-03") & date < as.Date("2018-10-04")]))%>%
  mutate(diff_mean = Wilson_aft - Wilson_bef,
         perc_mean = ((Wilson_aft - Wilson_bef)/ Wilson_bef)*100)
Wilson

Addison <- 
  cta2 %>%
  filter(stationname == "Addison-O'Hare") %>%
  group_by(month) %>%
  summarise(Addison_bef = mean(rides[date > as.Date("2014-09-30") & date < as.Date("2015-10-01")]),
            Addison_aft = mean(rides[date > as.Date("2016-11-30") & date < as.Date("2017-11-01")])) %>%
  mutate(diff_mean = Addison_aft - Addison_bef,
         perc_mean = ((Addison_aft - Addison_bef)/ Addison_bef)*100)
Addison

DanRyan <- 
  cta2 %>%
  filter(stationname == "95th/Dan Ryan") %>%
  group_by(month) %>%
  summarise(Dan_bef = mean(rides[date > as.Date("2016-02-29") & date < as.Date("2017-03-01")]),
            Dan_aft = mean(rides[date > as.Date("2019-01-31") & date < as.Date("2020-02-01")])) %>%
  mutate(diff_mean = Dan_aft - Dan_bef,
         perc_mean = ((Dan_aft - Dan_bef)/ Dan_bef)*100)
DanRyan
```

When using cbind it will include the month rows for each data set so I will need to join the data
sets using a join function so that they are joined by the month column.
```{r bind attempt}
cta3 <- 
  cbind(Cer_Chi, Clark_Div, Jarvis, Garfield, Wilson, Addison, DanRyan)

cta3 %>%
  kable()
```

I am unable to join all of the data together in one command so I have to add one each time.
```{r joining data sets}
join <- 
  left_join(Cer_Chi, Clark_Div, by = "month")
join

join1 <- 
  left_join(join, Jarvis)
join1

join2 <- 
  left_join(join1, Garfield, by = "month")
join2

join3 <- 
  left_join(join2, Wilson)
join3

join4 <- 
  left_join(join3, Addison, by = "month")
join4

CTA_data <- 
  left_join(join4, DanRyan)
CTA_data
```

```{r}
CTA_data %>%
  kable(col.names = c("Month", "Before", "After", "Diff Mean", "Perc Mean", "Before", "After", "Diff Mean", "Perc Mean", "Before", "After", 
                      "Diff Mean", "Perc Mean", 
                     "Before", "After", "Diff Mean", "Perc Mean", "Before", "After", "Diff Mean", "Perc Mean", "Before",  "After",
                     "Diff Mean", "Perc Mean", "Before", "After", "Diff Mean", "Perc Mean"),
        align = c("ccccccccccccccccccccccccccccc"),
        digits = c(0,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2),
        caption = "Average Daily Ridership for a Given Month Before and After CTA Project Completion") %>%
  
  kable_classic(font_size = 16,
                 html_font = "Times New Roman",
                 full_width = F) %>%
  add_header_above(c("", "Cer-Chinatown" = 4, "Clark/Division" = 4, "Jarvis" = 4,
                     "Garfield" = 4, "Wilson" = 4, "Addison" = 4, "95th/Dan Ryan" = 4))
```


To see our system wide changes
```{r system changes}
cta_system <- 
  cta %>%
  filter(daytype == "W") %>%
  mutate(date = as.Date(date),
         rides = as.numeric(rides),
         month = format(date, "%m"), year = format(date, "%Y"), day = format(date, "%d"))
```


```{r}
#cta %>%
  #filter(daytype == "W",
         #date <= as.Date("2013-12-31") & date >= as.Date("2012-12-01")) %>%
  #mutate(rides = as.numeric(rides)) %>% 
  #mutate(month = format(date, "%m"), year = format(date, "%Y"), day = format(date, "%d")) %>%
  #group_by(month, day) %>%
  #summarise(monthday_tot = sum(rides)) %>% 
  #group_by(month) %>% 
  #summarise(mean = mean(monthday_tot))

```



```{r }
System_Cermak <- 
  cta_system %>%
  group_by(month, day) %>%
  summarise(Mon_bef_Cermak = sum(rides[date > as.Date("2008-10-31") & date < as.Date("2009-11-01")]),
            Mon_aft_Cermak = sum(rides[date > as.Date("2011-03-31") & date < as.Date("2012-04-01")])) %>%
  group_by(month) %>%
  summarise(before_mean = mean(Mon_bef_Cermak),
            after_mean = mean(Mon_aft_Cermak)) %>%
  mutate(diff_mean = after_mean - before_mean,
         perc_mean = ((after_mean - before_mean)/ before_mean)*100)
System_Cermak

System_Clark_Division <- 
  cta_system %>%
  group_by(month, day) %>%
  summarise(Mon_bef_Clark_Division = sum(rides[date > as.Date("2011-08-31") & date < as.Date("2012-09-01")]),
            Mon_aft_Clark_Division = sum(rides[date > as.Date("2015-08-31") & date < as.Date("2016-09-01")])) %>%
  group_by(month) %>%
  summarise(before_mean = mean(Mon_bef_Clark_Division),
            after_mean = mean(Mon_aft_Clark_Division)) %>%
  mutate(diff_mean = after_mean - before_mean,
         perc_mean = ((after_mean - before_mean)/ before_mean)*100)
System_Clark_Division

System_Jarvis <- 
  cta_system %>%
  group_by(month, day) %>%
  summarise(Mon_bef_Jarvis = sum(rides[date > as.Date("2011-10-31") & date < as.Date("2012-11-01")]),
            Mon_aft_Jarvis = sum(rides[date > as.Date("2012-11-30") & date < as.Date("2013-12-01")])) %>%
  group_by(month) %>%
  summarise(before_mean = mean(Mon_bef_Jarvis),
            after_mean = mean(Mon_aft_Jarvis)) %>%
  mutate(diff_mean = after_mean - before_mean,
         perc_mean = ((after_mean - before_mean)/ before_mean)*100)
System_Jarvis

System_Garfield <- 
  cta_system %>%
  group_by(month, day) %>%
  summarise(Mon_bef_Garf = sum(rides[date > as.Date("2012-05-01") & date < as.Date("2013-05-01")]),
            Mon_aft_Garf = sum(rides[date > as.Date("2013-10-31") & date < as.Date("2014-11-01")])) %>%
  group_by(month) %>%
  summarise(before_mean = mean(Mon_bef_Garf),
            after_mean = mean(Mon_aft_Garf)) %>%
  mutate(diff_mean = after_mean - before_mean,
         perc_mean = ((after_mean - before_mean)/ before_mean)*100)
System_Garfield

System_Wilson <- 
  cta_system %>%
  group_by(month, day) %>%
  summarise(Mon_bef_Wilson = sum(rides[date > as.Date("2013-09-30") & date < as.Date("2014-10-01")]),
            Mon_aft_Wilson = sum(rides[date > as.Date("2017-09-30") & date < as.Date("2018-10-01")])) %>%
  group_by(month) %>%
  summarise(before_mean = mean(Mon_bef_Wilson),
            after_mean = mean(Mon_aft_Wilson)) %>%
  mutate(diff_mean = after_mean - before_mean,
         perc_mean = ((after_mean - before_mean)/ before_mean)*100)
System_Wilson

System_Addison <- 
  cta_system %>%
  group_by(month, day) %>%
  summarise(Mon_bef_Addison = sum(rides[date > as.Date("2014-09-30") & date < as.Date("2015-10-01")]),
            Mon_aft_Addison = sum(rides[date > as.Date("2016-11-30") & date < as.Date("2017-11-01")])) %>%
  group_by(month) %>%
  summarise(before_mean = mean(Mon_bef_Addison),
            after_mean = mean(Mon_aft_Addison)) %>%
  mutate(diff_mean = after_mean - before_mean,
         perc_mean = ((after_mean - before_mean)/ before_mean)*100)  
System_Addison

System_DanRyan <- 
  cta_system %>%
  group_by(month, day) %>%
  summarise(Mon_bef_Dan = sum(rides[date > as.Date("2016-02-29") & date < as.Date("2017-03-01")]),
            Mon_aft_Dan = sum(rides[date > as.Date("2019-01-31") & date < as.Date("2020-02-01")])) %>%
  group_by(month) %>%
  summarise(before_mean = mean(Mon_bef_Dan),
            after_mean = mean(Mon_aft_Dan)) %>%
  mutate(diff_mean = after_mean - before_mean,
         perc_mean = ((after_mean - before_mean)/ before_mean)*100)
System_DanRyan
```

```{r join system data}
sys_join <- 
rbind(System_Cermak, System_Clark_Division, System_Jarvis, System_Garfield, System_Wilson, System_Addison, System_DanRyan)
sys_join
```

```{r table the thing}
sys_join %>%
  kable() %>%
  kable_classic(font_size = 16,
                 html_font = "Times New Roman",
                 full_width = F) %>%
  pack_rows(index = c("Cermak-Chinatown" = 12, "Clark/Division" = 12, "Jarvis" = 12, 
                      "Garfield" = 12, "Wilson" = 12, "Addison" = 12, "95th/Dan Ryan" = 12))
```

