---
title: "PA 434 Final Project"
author: "Mia Krout & Jake da Silva Passos-Hoioos"
date: "4/25/2021"
output: pdf_document
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, message = F, warning = F, include = T)
```

# Introudction 

## Motivation and Research Questions

# Background

It is a well known fact that the City of Chicago is a city of neighborhoods. In total
Chicago has over 77 Community Areas, that roughly correspond (although they do not fully encapsulate) 
the many neighborhoods and communities within the city. It is also a well known fact that Chicago is a segregated city. Decades of practices such as
redlining, restrictive housing covenants, as well as outright legalized housing discrimination
has left the city with stark racial and ethnic boundaries that remain clear even
now. [Racial dot maps](http://www.radicalcartography.net/index.html?chicagodots) 
of the city are particularly revealing of the city's continued racial and ethnic 
homogeneity across the city, most predominately among Black Chicagoans on the South
and West Sides. Political boundaries, most notably,
[Congressional districts](https://upload.wikimedia.org/wikipedia/commons/thumb/b/be/United_States_Congressional_Districts_in_Illinois_%28metro_highli,ght%29%2C_2003_%E2%80%93_2013.tif/lossless-page1-400px-United_States_Congressional_Districts_in_Illinois_%28metro_highlight%29%2C_2003_%E2%80%93_2013.tif.png) take particularly unusual form in an effort to follow these tight boundaries. 

Acknowledging the extent of the city's segregated state is critical, as even the 
wishful or naive supposition that the city isn't segregated can have profound
consequences on the communities that have been historically marginalized and denied
equal opportunities and access. While the original motivation for this research was 
to study if there was a bias in the areas that the Chicago Transit Authority (CTA) 
was making improvements to the system (e.g., were improvements being made solely or predominately in White, wealthy, 
well educated neighborhoods). In further research of this topic, the answer to 
this question became clear: there in indeed within the areas served by the CTA, but
these are inherent biases that are the result of the years of institutional racism and 
bias towards communities of color. 

Consider the shape of the CTA system. It is a large radial systems with many lines 
radiating outward from the central downtown Loop. Lines radiate out in every direction 
but East due to Lake Michigan, but despite this, of the 10 different lines or branches
leaving the Loop, almost half of them (4) head North, while the remaining 6 lines
are equally divided heading South (3) and West (3). Looking back at a demographic 
map of the city this comes as no surprise, Chicago's densest, and Whitest areas 
are situated to the North of the Loop, that are traced by the Red, Brown, Purple, and in 
more recent years, Blue (along the Milwaukee Avenue Branch) lines. Meanwhile, on the South 
and West sides, the lines take on much different shapes, with two lines, the Red (Dan-Ryan Branch) and  Blue line (Forest Park Branch), 
being constructed in the medians of the interstate highways that were constructed during the post-war housing
boom. As many White households moved out of city areas in favor of suburban living, a phenomenon often refer to
as "White flight," the investment and focus on creating reliable transportation infrastructure left with them. 

Thus it became clear to us that if our research was merely seeking to see if there is in fact
a bias in the areas served by and the recipient of transportation improvement projects, that
our answer would be a **resounding yes.** While there is certainly still disagreement within the
subject as to *why* these inequities and biases exist, the fact remains that these inequities and 
biases exist in the first place. This research does not seek to find an answer or explanation for 
these inequities, but instead seeks to study them, to better understand them so that they 
can be more readily addressed and the historical wrongs to minority communities can be righted. 

# Research Question 

With the attention now turned towards better understanding the known inequities that
exist within the system, rather than answering the more existential question of whether
there is in fact an implicit bias to the system, the scope of our research comes 
more easily into view. If we accept the system as being the product of systems that 
were designed to benefit White communities at the expense of communities of color, 
then it is no surprise that improvements to the very same system will be similarly 
bias towards these communities. 

The new question that emerges is this: 

* If we accept that the system is inherently bias against communities of color, what 
effect would we expect these projects to have on ridership within these communities of color? 
 + We would expect that improvements made to Whiter, Richer, and more Educated areas would
 have a greater affect on ridership in these communities, while improvements made in communities 
 of color would less likely to see an increase in ridership. 
 + This would be especially if the improvements were viewed as being "perfomative" (i.e., simply 
 to create the appearance that others are concerned with the issue rather than actually being concerned 
 with the outcome.)
 
 
In order to address this question there are two key sets of data we need to analyze: 

* Demographics of neighborhoods where CTA system improvements have been made.
* Ridership statistics for these areas (stations) before and after the improvements were made. 

To study the demographic data of the areas subject to CTA improvements, we will 
utilize data made available by the [American Community Survey (ACS)](https://www.census.gov/programs-surveys/acs/about.html), a demography 
study program conducted by the U.S. Census Bureau. Conveniently, Chicago's 77 community 
areas correspond to the census tract group areas used by the Census, such that tract
level census data can be easily aggregated to the neighborhood level due to the tract boundaries
aligning with the community area boundaries. 

**An important note** regarding ACS estimate values: The ACS estimates utilized for 
the purposes of this research are the **5-year estimates.** This means that the estimated
values used in this project are the ACS estimates for a given census tract for the 5 year-period spanning
from 2005 to 2010. Although these estimates will be frequently referred to as the **2010 estimates**
or **2010 5 year estimates** the estimate values are reflective of the estimated value for the entire 5 year period 
(i.e., 2005 to 2010) not simply the year 2010.

To identify the specific improvement projects of interest, the [CTAs list](https://www.transitchicago.com/newsprojects/system-improvement-projects/completed-station-projects) of past projects
was reviewed. From this list a deliberate sample was selected with the intent to ensure 
that the group of improvements was a heterogeneous group with demographics comparable to the 
city at large. The goal of this is to then compare the differences in ridership from before and after the improvement
was made to see if there were any meaningful differences across the different groups, for example, if projects in predominantly White neighborhoods have a greater impact on ridership than those made in predominately minority neighborhoods. 

To see if there were any meaninful changes in the ridership before and after the improvement was made, the CTA's publicly available [daily ridership dataset](https://data.cityofchicago.org/Transportation/CTA-Ridership-L-Station-Entries-Daily-Totals/5neh-572f) that provides the daily number of station entries for each station from 2001 to present. 

# Data Prep and Cleaning - Census Data

```{r Packages}
# install.packages("tidyverse")
# install.packages("censusapi")

library(tidyverse) 
library(censusapi)
library(kableExtra)
#install.packages("threeparttablex", repos = "http://cran.us.r-project.org"

```

**Please Note**: The Census Bureau requires users to obtain their own
personal API key. The code chunk titled "API Key" contains an empty
string for you to insert your own API key. This chunk has been excluded
from the text of this report for brevity.

```{r API, include=F}
# Only run the below the first time you are setting up the API key
#
# Insert your actual API Key before runing if not Mia or Jake
Sys.setenv(CENSUS_KEY = "072a5932353383e73bef59d5792a0c5c93940755")
#
readRenviron("~/.Renviron")
Sys.getenv("CENSUS_KEY")

```

The package censusapi contains metadata about each of the available APIs
and the data accessible from said APIs, and can be quite useful when
trying to identify the relevant data set.

```{r Looking at Data}
apis <- listCensusApis()

view(apis)

project_vars <- listCensusMetadata(
  name = "acs/acs5", 
  vintage = 2019,
  type = "variables",
)

project_geo <- listCensusMetadata(name = "dec/sf1", vintage = 2010, type = "geography")

head(project_geo)
```

```{r  Calling Data}

demo_2010 <- as_tibble(
  getCensus(name = "acs/acs5", # name specifies the census data, in this case the ACS 5 year ests.  
            vintage = 2010, # For non-time series data vintage = year 
            vars = c("NAME", # Provides name of jurisdiction (here tracts)
                     "B03002_001E", ### Total Race/Ethnicity 
                     "B03002_002E", # Total Non-Hispanic
                     "B03002_003E", # Non-Hispanic White
                     "B03002_004E", # Non-Hispanic Black
                     "B03002_005E", # Non-Hispanic Native American
                     "B03002_006E", # Non-Hispanic Asian
                     "B03002_007E", # Non-Hispanic Hawaiian or Pacific Islander
                     "B03002_008E", # Non-Hispanic Other
                     "B03002_009E", # Non-Hispanic Two or more races (Multiracial)
                     "B03002_012E", # Total Hispanic
                     "B03002_013E", # Hispanic White
                     "B03002_014E", # Hispanic Black
                     "B03002_015E", # Hispanic Native American
                     "B03002_016E", # Hispanic Asian
                     "B03002_017E", # Hispanic Hawaiian or Pacific Islander
                     "B03002_018E", # Hispanic Other 
                     "B03002_019E", # Hispanic Two or more races (Multiracial)
                     "B15002_001E", # Total Educ
                     "B15002_002E", # Total Educ - Males
                     "B15002_003E", # Males Less than HS 
                     "B15002_004E", # Males Less than HS 
                     "B15002_005E", # Males Less than HS 
                     "B15002_006E", # Males Less than HS 
                     "B15002_007E", # Males Less than HS 
                     "B15002_008E", # Males Less than HS 
                     "B15002_009E", # Males Less than HS 
                     "B15002_010E", # Males Less than HS
                     "B15002_011E", # Males HS or some college 
                     "B15002_012E", # Males HS or some college
                     "B15002_013E", # Males HS or some college
                     "B15002_014E", # Males College degree +  
                     "B15002_015E", # Males College degree + 
                     "B15002_016E", # Males College degree +
                     "B15002_017E", # Males College degree + 
                     "B15002_018E", # Males College degree + 
                     "B15002_019E", # Total Educ - Females
                     "B15002_020E", # Females Less than HS 
                     "B15002_021E", # Females Less than HS 
                     "B15002_022E", # Females Less than HS 
                     "B15002_023E", # Females Less than HS 
                     "B15002_024E", # Females Less than HS 
                     "B15002_025E", # Females Less than HS 
                     "B15002_026E", # Females Less than HS 
                     "B15002_027E", # Females Less than HS 
                     "B15002_028E", # Females HS or some college
                     "B15002_029E", # Females HS or some college
                     "B15002_030E", # Females HS or some college
                     "B15002_031E", # Females College degree + 
                     "B15002_032E", # Females College degree +
                     "B15002_033E", # Females College degree +
                     "B15002_034E", # Females College degree +
                     "B15002_035E", # Females College degree +
                     "B16001_001E", ### Total Language Spoken at Home
                     "B16001_002E", # English only
                     "B16001_003E", # Spanish Total
                     "B16001_004E", # Spanish, English Very Well 
                     "B16001_005E", # Spanish, English Less Than Very Well  
                     "B16001_036E", # Polish Total
                     "B16001_037E", # Polish, English Very Well  
                     "B16001_038E", # Polish, English Less Than Very Well  
                     "B16001_066E", # Chinese Total 
                     "B16001_067E", # Chinese, English Very Well 
                     "B16001_068E", # Chinese, English Less Than Very Well 
                     "B16001_093E", # Tagalog (incl. Filipino) Total
                     "B16001_094E", # Tagalog, English Very Well
                     "B16001_095E", # Tagalog, English Less Than Very Well
                     "B16001_108E", # Arabic Total
                     "B16001_109E", # Arabic, English Very Well
                     "B16001_110E", # Arabic, English Less Than Very Well
                     "B19013_001E"), # Median Income
            region = "tract:*", # Indicates we want tract level data 
            regionin =  "state:17+county:031")  # ID State and County using FIPS
)

```

Public census data is available at various jurisdiction levels, from
multi-state regions down to individual block groups. For our project,
our interest was on Chicago community areas, which approximate Chicago's
various neighborhoods. Each of these areas are comprised of many
individual census tracts. For our analysis, we used maps published by
the City of Chicago identifying each community area and the census
tracts that comprise that community. After identifying each of the
community areas for each improvement project, we then used the
identified census tracts to calculate the approximate populations of
each community.

```{r Cleaning Data}

chicago_2010 <- demo_2010 %>% 
  rename(re_total = B03002_001E,
         nh_total = B03002_002E,
         nh_white = B03002_003E, 
         nh_black = B03002_004E,
         nh_native = B03002_005E, 
         nh_asian = B03002_006E, 
         nh_pi = B03002_007E, 
         nh_other = B03002_008E,
         nh_multi = B03002_009E,
         h_total = B03002_012E, 
         h_white = B03002_013E, 
         h_black = B03002_014E, 
         h_native = B03002_015E, 
         h_asian = B03002_016E, 
         h_pi = B03002_017E, 
         h_other = B03002_018E,
         h_multi = B03002_019E, 
         lang_total = B16001_001E, 
         eng = B16001_002E, 
         sp_total = B16001_003E,
         sp_gd_eng = B16001_004E, 
         sp_bd_eng = B16001_005E, 
         plsk_total = B16001_036E,
         plsk_gd_eng = B16001_037E,
         plsk_bd_eng = B16001_038E, 
         chn_total = B16001_066E, 
         chn_gd_eng = B16001_067E, 
         chn_bd_eng = B16001_068E, 
         flp_total = B16001_093E,
         flp_gd_eng = B16001_094E, 
         flp_bd_eng = B16001_095E, 
         arab_total = B16001_108E, 
         arab_gd_eng = B16001_109E, 
         arab_bd_eng = B16001_110E, 
         edu_total = B15002_001E, 
         median_income = B19013_001E) %>%
  mutate(native_gd_eng = eng + sp_gd_eng + plsk_gd_eng + chn_gd_eng + flp_gd_eng + arab_gd_eng,
         not_eng = sp_total + plsk_total + chn_total + flp_total + arab_total, 
         bd_eng = sp_bd_eng + plsk_bd_eng + chn_bd_eng + flp_bd_eng + arab_bd_eng, 
         no_hs = B15002_003E + B15002_004E + B15002_005E + B15002_006E + B15002_007E +
         B15002_008E + B15002_009E + B15002_010E + B15002_020E + B15002_021E + B15002_022E + 
         B15002_023E + B15002_024E + B15002_025E + B15002_026E + B15002_027E,
         hs = B15002_011E + B15002_012E + B15002_013E + B15002_028E + B15002_029E + B15002_030E,
         uni = B15002_014E + B15002_015E + B15002_016E + B15002_017E + B15002_018E + B15002_031E + B15002_032E + B15002_033E + B15002_034E + B15002_035E, 
         ) %>%
  select(everything(), -matches("B15002")) %>% 
  mutate(tract = as.numeric(tract), .keep = "unused") %>% 
  filter((tract >= 010100 & tract <= 750600) | tract == 760800
         | (tract >= 770500 & tract <= 770700) | tract == 770900 | tract == 810400
         | (tract >= 810400 & tract <= 810600) | tract == 810600 | tract == 811600
         | tract == 823304 | tract == 820902 | tract == 811600 | tract == 840000 
         |  tract == 840801) %>% # Filter only for tracts in Chicago
  filter(tract != 381700) %>% # This tract has no one in it and weird negative income values
  mutate(neighborhood = if_else((tract >= 010100) & (tract <= 010999),
                                "RODGERS PARK",
                                if_else((tract >= 031000) & (tract <= 032199),
                                        "UPTOWN", 
                                        if_else((tract >= 080100) & (tract <= 081999), 
                                                "NEAR NORTH SIDE",
                                                if_else((tract >= 210100) & (tract <= 210999),
                                                        "AVONDALE", 
                                                        if_else((tract >= 340100) & (tract <= 340699), 
                                                                "ARMOUR SQUARE", 
                                                                if_else((tract >= 680100) & (tract <= 681499), 
                                                                        "ENGLEWOOD", 
                                                                        ifelse((tract >= 490100) & (tract <= 491499), 
                                                                                "ROSEWOOD",
                                                                                "REST OF CITY") # Rest of Chicago. 
                                                                        )
                                                                )
                                                        )
                                                )
                                        )
                                )
         ) 

chicago_2010
  
```

```{r Reviewing data}

mm_inc <- chicago_2010 %>% 
  filter(neighborhood != "REST OF CITY") %>%
  group_by(neighborhood) %>%
  select(neighborhood, median_income) %>% 
  summarise(mean_median_income = mean(median_income)) %>% 
  select(mean_median_income)
  
city_inc <- chicago_2010 %>% 
  select(median_income) %>% 
  summarise(mean_median_income = mean(median_income))

cta_inc <- chicago_2010 %>% 
  filter(neighborhood != "REST OF CITY") %>%
  select(median_income) %>% 
  summarise(mean_median_income = mean(median_income))

#chicago_2010 %>% 
#  select(everything(), -tract, -median_income) %>% 
#  group_by(neighborhood) %>% 
#  summarise(across(everything()), mean)

city_per <- chicago_2010 %>% 
  select(everything(), -tract, -median_income) %>% 
  summarise(across(where(is.numeric), sum)) %>% 
  transmute(native_gd_per = (native_gd_eng / lang_total) * 100, 
         bd_eng_per = (bd_eng / lang_total) * 100,
         not_eng_per = (not_eng / lang_total) * 100,
         primary_sp = (sp_total / lang_total) * 100,
         no_hs_per = (no_hs / edu_total) * 100,
         hs_per = (hs / edu_total) * 100,
         uni_per = (uni / edu_total) * 100, 
         nh_white_per = (nh_white / re_total) * 100,
         h_white_per = (h_white / re_total) * 100, # Need to make note that only NH White and H White are separated, all others are combined
         black_per = ((nh_black + h_black) / re_total) * 100,
         aapi_per = ((nh_asian + h_asian + nh_pi + h_pi) / re_total) * 100, # Also note combo of Asian and Pacific Islander (AAPI)
         othermulti_per = (((nh_other + h_other + nh_multi + h_multi) / re_total) * 100)  # Make note of combo of other race and multi racial
  ) 

city_wide <- cbind("CITY WIDE", city_per, city_inc) %>% 
  rename(neighborhood = `"CITY WIDE"`)

cta_per <- chicago_2010 %>% 
  filter(neighborhood != "REST OF CITY") %>%
  select(everything(), -tract, -median_income) %>% 
  summarise(across(where(is.numeric), sum)) %>% 
  transmute(native_gd_per = (native_gd_eng / lang_total) * 100, 
         bd_eng_per = (bd_eng / lang_total) * 100,
         not_eng_per = (not_eng / lang_total) * 100,
         primary_sp = (sp_total / lang_total) * 100,
         no_hs_per = (no_hs / edu_total) * 100,
         hs_per = (hs / edu_total) * 100,
         uni_per = (uni / edu_total) * 100, 
         nh_white_per = (nh_white / re_total) * 100,
         h_white_per = (h_white / re_total) * 100, 
         black_per = ((nh_black + h_black) / re_total) * 100,
         aapi_per = ((nh_asian + h_asian + nh_pi + h_pi) / re_total) * 100, 
         othermulti_per = (((nh_other + h_other + nh_multi + h_multi) / re_total) * 100)  
  )

cta_wide <- cbind("AREAS WITH CTA IMPROVEMENT", cta_per, cta_inc) %>% 
  rename(neighborhood = `"AREAS WITH CTA IMPROVEMENT"`)
  

percents <- chicago_2010 %>% 
  select(everything(), -tract, -median_income) %>%
  filter(neighborhood != "REST OF CITY") %>%
  group_by(neighborhood) %>% 
  summarise(across(where(is.numeric), sum)) %>% 
  transmute(neighborhood = neighborhood,
         native_gd_per = (native_gd_eng / lang_total) * 100, 
         bd_eng_per = (bd_eng / lang_total) * 100,
         not_eng_per = (not_eng / lang_total) * 100,
         primary_sp = (sp_total / lang_total) * 100,
         no_hs_per = (no_hs / edu_total) * 100,
         hs_per = (hs / edu_total) * 100,
         uni_per = (uni / edu_total) * 100, 
         nh_white_per = (nh_white / re_total) * 100,
         h_white_per = (h_white / re_total) * 100, # Need to make note that only NH White and H White are separated, all others are combined
         black_per = ((nh_black + h_black) / re_total) * 100,
         aapi_per = ((nh_asian + h_asian + nh_pi + h_pi) / re_total) * 100, # Also note combo of Asian and Pacific Islander (AAPI)
         othermulti_per = (((nh_other + h_other + nh_multi + h_multi) / re_total) * 100)  # Make note of combo of other race and multi racial
  ) %>% 
  cbind(mm_inc) %>%
  rbind(cta_wide, city_wide)


percents$neighborhood <- str_to_title(percents$neighborhood)
```

```{r Lang check}
# English and Spanish are going to be highest but let's see how our neighborhoods 
# do in terms of the other languages from Chicago's top 6. 

lang <- chicago_2010 %>% 
  select(everything(), -tract, -median_income) %>%
  filter(neighborhood != "REST OF CITY") %>%
  group_by(neighborhood) %>% 
  summarise(across(where(is.numeric), sum)) %>%
  select(neighborhood, lang_total:sp_total, plsk_total, chn_total, flp_total, arab_total) %>%
  transmute(neighborhood = neighborhood,
            eng_only = round((eng / lang_total) * 100, 2), 
            primary_sp = round((sp_total / lang_total) * 100, 2), 
            primary_plsk = round((plsk_total / lang_total) * 100, 2), 
            primary_chn = round((chn_total / lang_total) * 100, 2), 
            primary_flp = round((flp_total / lang_total) * 100, 2), 
            primary_arab = round((arab_total / lang_total) * 100, 2)) 

city_lang <- chicago_2010 %>% 
  select(everything(), -tract, -median_income) %>% 
  summarise(across(where(is.numeric), sum)) %>% 
  transmute(eng_only = round((eng / lang_total) * 100, 2), 
            primary_sp = round((sp_total / lang_total) * 100, 2), 
            primary_plsk = round((plsk_total / lang_total) * 100, 2), 
            primary_chn = round((chn_total / lang_total) * 100, 2), 
            primary_flp = round((flp_total / lang_total) * 100, 2), 
            primary_arab = round((arab_total / lang_total) * 100, 2))

city_lang <- cbind("CITY WIDE", city_lang) %>% 
  rename(neighborhood = `"CITY WIDE"`)

dim(lang)
dim(city_lang)

all_lang <- rbind(lang, city_lang)

all_lang

# Only thing interesting is the 6% in Avondale given it's higher than the city-wide average
# Everything else is what we would expect (high amount of Chinese spoken in Armour Square 
# since Chinatown is there) and Avondale being primary Spanish, and Englewood and Rosewood being
# almost entirely English (since it's 98% AA). Also Near North Side is predictably higher 
# than city average for English. 

```

# Demographics Charts

```{r Table of Race Data, echo=T, include=T}

percents  %>%
  select(neighborhood, nh_white_per:othermulti_per) %>%
  kable(col.names = c("Area",
                      "Non-Hisp White", "Hisp White", "Black", "AAPI", "Other/Multiracial"), 
        align = "ccc", 
        caption = "Racial Composition of Neighborhoods where CTA Improvements were Made, and City-Wide Values",
        digits = 2, 
        format.args = list(big.mark = ",")) %>%
  kable_styling(latex_options = c("striped", "scale_down"))

```

```{r Table of Lang Data, echo=T, include=T}

percents  %>%
  select(neighborhood,  native_gd_per:primary_sp) %>%
  kable(col.names = c("Area",
                      "English Native or Very Well", "English Less than Very Well", "Primary not English", "Primary Language Spanish"), 
        align = "ccc", 
        caption = "Language Composition of Neighborhoods where CTA Improvements were Made, and City-Wide Values",
        digits = 2, 
        format.args = list(big.mark = ",")) %>%
  kable_styling(latex_options = c("striped", "scale_down"))

```

```{r Table of Edu Data, echo=T, include=T}

percents  %>%
  select(neighborhood, no_hs_per:uni_per) %>%
  kable(col.names = c("Area",
                      "Less Than a HS", "HS + Some College", "College Degree"), 
        align = "ccc", 
        caption = "Educational Attainment of Neighborhoods where CTA Improvements were Made, and City-Wide Values",
        digits = 2, 
        format.args = list(big.mark = ",")) %>%
  kable_styling(latex_options = c("striped", "scale_down"))

```


```{r Table of Income, echo=T, include=T}

percents  %>%
  select(neighborhood, mean_median_income) %>%
  kable(col.names = c("Area",
                      "Mean Median Income*"), 
        align = "ccc", 
        caption = "Demographics of Neighborhoods where CTA Improvements were Made, and City-Wide Values",
        digits = 2, 
        format.args = list(big.mark = ",")) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  add_footnote("Value in Real 2010 USD; Values were calculated by taking the median income of each census tract and then taking the average among tracts in a given neighborhood or across all tracts")



```

City of Chicago's population in 2010 was 2.6 million, and this estimates
2.4 so we are fairly close, a tract or two along the edges may have been
excluded, but the bulk of the city's population is here in the data set.

```{r Checking Data}



```

```{r Further Checking}

```
