---
title: "Final Project"
author: "Mia Krout & Jake da Silva Passos-Hoioos"
date: "4/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, include = T)
```

# Introduction 

# Data Prep and Cleaning 

```{r Packages}
# install.packages("tidyverse")
# install.packages("censusapi")

library(tidyverse) 
library(censusapi)
```

**Please Note**: The Census Bureau requires users to obtain their own personal API 
key. The code chunk titled "API Key" contains an empty string for you to insert
your own API key. This chunk has been excluded from the text of this report for 
brevity. 

```{r API, include=F}
# Only run the below the first time you are setting up the API key
#
# Insert your actual API Key before runing if not Mia or Jake
Sys.setenv(CENSUS_KEY = "072a5932353383e73bef59d5792a0c5c93940755")
#
readRenviron("~/.Renviron")
Sys.getenv("CENSUS_KEY")

```

The package censusapi contains metadata about each of the available APIs and the 
data accessible from said APIs, and can be quite useful when trying to identify
the relevant data set. 

```{r Looking at Data, include=T}
apis <- listCensusApis()

view(apis)

project_vars <- listCensusMetadata(
  name = "acs/acs5", 
  vintage = 2019,
  type = "variables",
)

project_geo <- listCensusMetadata(name = "dec/sf1", vintage = 2010, type = "geography")

head(project_geo)
```

```{r  Calling Data, include=T}

# NEED TO DEFINE DEMO VARS 

demo_2010 <- as_tibble(
  getCensus(name = "acs/acs5", # name specifies the census data, in this case the ACS 5 year ests.  
            vintage = 2010, # For non-time series data vintage = year 
            vars = c("NAME", # Provides name of jurisdiction (here tracts)
                     "B03002_001E", ### Total Race/Ethnicity 
                     "B03002_002E", # Total Non-Hispanic
                     "B03002_003E", # Non-Hispanic White
                     "B03002_004E", # Non-Hispanic Black
                     "B03002_005E", # Non-Hispanic Native American
                     "B03002_006E", # Non-Hispanic Asian
                     "B03002_007E", # Non-Hispanic Hawaiian or Pacific Islander
                     "B03002_008E", # Non-Hispanic Other
                     "B03002_009E", # Non-Hispanic Two or more races (Multiracial)
                     "B03002_012E", # Total Hispanic
                     "B03002_013E", # Hispanic White
                     "B03002_014E", # Hispanic Black
                     "B03002_015E", # Hispanic Native American
                     "B03002_016E", # Hispanic Asian
                     "B03002_017E", # Hispanic Hawaiian or Pacific Islander
                     "B03002_018E", # Hispanic Other 
                     "B03002_019E", # Hispanic Two or more races (Multiracial)
                     "B15002_001E", # Total Educ
                     "B15002_002E", # Total Educ - Males
                     "B15002_003E", # Males Less than HS 
                     "B15002_004E", # Males Less than HS 
                     "B15002_005E", # Males Less than HS 
                     "B15002_006E", # Males Less than HS 
                     "B15002_007E", # Males Less than HS 
                     "B15002_008E", # Males Less than HS 
                     "B15002_009E", # Males Less than HS 
                     "B15002_010E", # Males Less than HS
                     "B15002_011E", # Males HS or some college 
                     "B15002_012E", # Males HS or some college
                     "B15002_013E", # Males HS or some college
                     "B15002_014E", # Males College degree +  
                     "B15002_015E", # Males College degree + 
                     "B15002_016E", # Males College degree +
                     "B15002_017E", # Males College degree + 
                     "B15002_018E", # Males College degree + 
                     "B15002_019E", # Total Educ - Females
                     "B15002_020E", # Females Less than HS 
                     "B15002_021E", # Females Less than HS 
                     "B15002_022E", # Females Less than HS 
                     "B15002_023E", # Females Less than HS 
                     "B15002_024E", # Females Less than HS 
                     "B15002_025E", # Females Less than HS 
                     "B15002_026E", # Females Less than HS 
                     "B15002_027E", # Females Less than HS 
                     "B15002_028E", # Females HS or some college
                     "B15002_029E", # Females HS or some college
                     "B15002_030E", # Females HS or some college
                     "B15002_031E", # Females College degree + 
                     "B15002_032E", # Females College degree +
                     "B15002_033E", # Females College degree +
                     "B15002_034E", # Females College degree +
                     "B15002_035E", # Females College degree +
                     "B16001_001E", ### Total Language Spoken at Home
                     "B16001_002E", # English only
                     "B16001_003E", # Spanish Total
                     "B16001_004E", # Spanish, English Very Well 
                     "B16001_005E", # Spanish, English Less Than Very Well  
                     "B16001_036E", # Polish Total
                     "B16001_037E", # Polish, English Very Well  
                     "B16001_038E", # Polish, English Less Than Very Well  
                     "B16001_066E", # Chinese Total 
                     "B16001_067E", # Chinese, English Very Well 
                     "B16001_068E", # Chinese, English Less Than Very Well 
                     "B16001_093E", # Tagalog (incl. Filipino) Total
                     "B16001_094E", # Tagalog, English Very Well
                     "B16001_095E", # Tagalog, English Less Than Very Well
                     "B16001_108E", # Arabic Total
                     "B16001_109E", # Arabic, English Very Well
                     "B16001_110E", # Arabic, English Less Than Very Well
                     "B19013_001E"), # Median Income
            region = "tract:*", # Indicates we want tract level data 
            regionin =  "state:17+county:031")  # ID State and County using FIPS
)

```

Public census data is available at various jurisdiction levels, from multi-state
regions down to individual block groups. For our project, our interest was on Chicago
community areas, which approximate Chicago's various neighborhoods. Each of these areas
are comprised of many individual census tracts. For our analysis, we used maps published
by the City of Chicago identifying each community area and the census tracts that
comprise that community. After identifying each of the community areas for each
improvement project, we then used the identified census tracts to calculate the
approximate populations of each community. 


```{r Cleaning Data}


chicago_2010 <- demo_2010 %>% 
  rename(re_total = B03002_001E,
         nh_total = B03002_002E,
         nonh_white = B03002_003E, 
         nh_black = B03002_004E,
         nh_native = B03002_005E, 
         nh_asian = B03002_006E, 
         nh_pi = B03002_007E, 
         nh_other = B03002_008E,
         nh_multi = B03002_009E,
         h_total = B03002_012E, 
         h_white = B03002_013E, 
         h_black = B03002_014E, 
         h_native = B03002_015E, 
         h_asian = B03002_016E, 
         h_pi = B03002_017E, 
         h_other = B03002_018E,
         his_multi = B03002_019E, 
         lang_total = B16001_001E, 
         eng = B16001_002E, 
         sp_total = B16001_003E,
         sp_gd_eng = B16001_004E, 
         sp_bd_eng = B16001_005E, 
         plsk_total = B16001_036E,
         plsk_gd_eng = B16001_037E,
         plsk_bd_eng = B16001_038E, 
         chn_total = B16001_066E, 
         chn_gd_eng = B16001_067E, 
         chn_bd_eng = B16001_068E, 
         flp_total = B16001_093E,
         flp_gd_eng = B16001_094E, 
         flp_bd_eng = B16001_095E, 
         arab_total = B16001_108E, 
         arab_gd_eng = B16001_109E, 
         arab_bd_eng = B16001_110E, 
         edu_total = B15002_001E, 
         median_income = B19013_001E) %>%
  mutate(native_gd_eng = eng + sp_gd_eng + plsk_gd_eng + chn_gd_eng + flp_gd_eng + arab_gd_eng,
         not_eng = sp_total + plsk_total + chn_total + flp_total + arab_total, 
         bd_eng = sp_bd_eng + plsk_bd_eng + chn_bd_eng + flp_bd_eng + arab_bd_eng, 
         no_hs = B15002_003E + B15002_004E + B15002_005E + B15002_006E + B15002_007E +
         B15002_008E + B15002_009E + B15002_010E + B15002_020E + B15002_021E + B15002_022E + 
         B15002_023E + B15002_024E + B15002_025E + B15002_026E + B15002_027E,
         hs = B15002_011E + B15002_012E + B15002_013E + B15002_028E + B15002_029E + B15002_030E,
         uni = B15002_014E + B15002_015E + B15002_016E + B15002_017E + B15002_018E + B15002_031E + B15002_032E + B15002_033E + B15002_034E + B15002_035E, 
         ) %>%
  select(everything(), -matches("B15002")) %>% 
  mutate(tract = as.numeric(tract), .keep = "unused") %>% 
  filter((tract >= 010100 & tract <= 750600) | tract == 760800
         | (tract >= 770500 & tract <= 770700) | tract == 770900 | tract == 810400
         | (tract >= 810400 & tract <= 810600) | tract == 810600 | tract == 811600
         | tract == 823304 | tract == 820902 | tract == 811600 | tract == 840000 
         |  tract == 840801) %>% # Filter only for tracts in Chicago
  filter(tract != 381700) %>% # This tract has no one in it and weird negative income values
  mutate(neighborhood = if_else((tract >= 010100) & (tract <= 010999),
                                "RODGERS PARK",
                                if_else((tract >= 031000) & (tract <= 032199),
                                        "UPTOWN", 
                                        if_else((tract >= 080100) & (tract <= 081999), 
                                                "NEAR NORTH SIDE",
                                                if_else((tract >= 210100) & (tract <= 210999),
                                                        "AVONDALE", 
                                                        if_else((tract >= 340100) & (tract <= 340699), 
                                                                "ARMOUR SQUARE", 
                                                                if_else((tract >= 680100) & (tract <= 681499), 
                                                                        "ENGLEWOOD", 
                                                                        ifelse((tract >= 490100) & (tract <= 491499), 
                                                                                "ROSEWOOD",
                                                                                "REST OF CITY") # Rest of Chicago. 
                                                                        )
                                                                )
                                                        )
                                                )
                                        )
                                )
         ) 

chicago_2010
  
```

```{r Reviewing data} 

mm_inc <- chicago_2010 %>% 
  group_by(neighborhood) %>%
  select(neighborhood, median_income) %>% 
  summarise(mean_median_income = mean(median_income)) %>% 
  select(mean_median_income)
  


chicago_2010 %>% 
  select(everything(), -tract, -median_income) %>% 
  group_by(neighborhood) %>% 
  summarise(across(everything()), mean)


sum(chicago_2010$race_eth_total)

chicago_2010 %>% 
  select(everything(), -tract, -median_income) %>% 
  group_by(neighborhood) %>% 
  summarise(across(where(is.numeric), sum)) %>% 
  cbind(mm_inc) %>% 
  mutate(native_gd_perc = (native_gd_eng / lang_total), 
         no_hs_perc = (no_hs / edu_total),
         hs_perc = (hs / edu_total),
         uni_perc = (uni / edu_total), 
         nh_white_per = (nh_white / re_total),
         h_white_per = (h_white / re_total), # Need to make note that only NH White and H White are separated, all others are combined
         black_per = ((nh_black + h_black) / re_total),
         aapi_per = ((nh_asian + h_asian + nh_pi + h_pi) / re_total), # Also note combo of Asian and Pacific Islander (AAPI)
         othermulti_per = ((nh_other h_other + nh_multi + h_multi) / re_total), # Make note of combo of other race and multi racial
         
          
  )

```



City of Chicago's population in 2010 was 2.6 million, and this estimates 2.4 so 
we are fairly close, a tract or two along the edges may have been excluded, but 
the bulk of the city's population is here in the data set. 
```{r Checking Data, include=T}

demo_2010

```


```{r Further Checking, include=T}
demo_2010 %>% 
  filter(neighborhood == "ENGLEWOOD") %>%
  print()


sum(demo_2010$h_native)
```

